Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@

```{r}
d_journals <- d_journals %>%
  select(timestamps = Timestamp,
         coder_id = `Coder's Initials`,
         pilot = `Are you piloting?`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         A_ppc_name = `A. Enter the name of the PPC type offered by the journal:`,
         B_ppc_name = `B. Enter the name of the PPC type offered by the journal:`,
         C_ppc_name = `C. Enter the name of the PPC type offered by the journal:`,
         A_ppc_description = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         B_ppc_description = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         C_ppc_description = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         A_ppc_length = `A. Are there any length limits for this type of PPC?`,
         B_ppc_length = `B. Are there any length limits for this type of PPC?`,
         C_ppc_length = `C. Are there any length limits for this type of PPC?`,
         A_ppc_time = `A. Are there any time limits for submission of this type of PPC?`,
         B_ppc_time = `B. Are there any time limits for submission of this type of PPC?`,
         C_ppc_time = `C. Are there any time limits for submission of this type of PPC?`,
         A_ppc_ref = `A. Are there any reference limits for this type of PPC?`,
         B_ppc_ref = `B. Are there any reference limits for this type of PPC?`,
         C_ppc_ref = `C. Are there any reference limits for this type of PPC?`,
         A_ppc_review = `A. Is this type of PPC sent for independent external peer review?`,
         B_ppc_review = `B. Is this type of PPC sent for independent external peer review?`,
         C_ppc_review = `C. Is this type of PPC sent for independent external peer review?`,
         A_ppc_note = `A. Anything additional, unusual, or interesting to note?`,
         B_ppc_note = `B. Anything additional, unusual, or interesting to note?`,
         C_ppc_note = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "),
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

>>>>

# Convert raw data to primary data

This will be moved to master script later.

```{r}
source(here('analysis','raw_to_primary.R')) # converts raw data to primary data
```

@@

```{r}
d_journals <- d_journals %>%
  select(timestamps = Timestamp,
         coder_id = `Coder's Initials`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         A_ppc_name = `A. Enter the name of the PPC type offered by the journal:`,
         B_ppc_name = `B. Enter the name of the PPC type offered by the journal:`,
         C_ppc_name = `C. Enter the name of the PPC type offered by the journal:`,
         A_ppc_description = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         B_ppc_description = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         C_ppc_description = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         A_ppc_length = `A. Are there any length limits for this type of PPC?`,
         B_ppc_length = `B. Are there any length limits for this type of PPC?`,
         C_ppc_length = `C. Are there any length limits for this type of PPC?`,
         A_ppc_time = `A. Are there any time limits for submission of this type of PPC?`,
         B_ppc_time = `B. Are there any time limits for submission of this type of PPC?`,
         C_ppc_time = `C. Are there any time limits for submission of this type of PPC?`,
         A_ppc_ref = `A. Are there any reference limits for this type of PPC?`,
         B_ppc_ref = `B. Are there any reference limits for this type of PPC?`,
         C_ppc_ref = `C. Are there any reference limits for this type of PPC?`,
         A_ppc_review = `A. Is this type of PPC sent for independent external peer review?`,
         B_ppc_review = `B. Is this type of PPC sent for independent external peer review?`,
         C_ppc_review = `C. Is this type of PPC sent for independent external peer review?`,
         A_ppc_note = `A. Anything additional, unusual, or interesting to note?`,
         B_ppc_note = `B. Anything additional, unusual, or interesting to note?`,
         C_ppc_note = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "),
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))
